\Large \bf \projtitle

### 2015-05-07 doc/paper/paper.tex
finished reddit effect section
added placeholders to results section

\subsection{DOM injection layer}
The DOM injection layer facilitates the link between the DOM as displayed in the browser and the entire peer-to-peer system. The DOM injection layer creates a websocket, and then instantiates a Tracker and Signaling Channel. It uses these to then instantiate a Connection Manager and in turn, uses this to instantiate a Download Manager.

@@

\section{Server implementation}

@@

\subsection{Tracker}
The tracker is hosted on a remote server and tracks client connections.
The client-side tracker interface opens a WebSocket connection with the remote tracker,
which registers the existence of this client. The remote tracker responds to
requests from the client for lists of peers with a given resource. When a client
publicizes that it has a resource through the tracker interface, the remote tracker updates
the list of peers with the resource to include this client, as
long as its WebSocket connection remains open. Upon WebSocket disconnection,
the tracker ``forgets'' about the client and erases all data about the client's
held resources.

\subsection{WebRTC handshake channel}

@@

We tested \zbf on a simple site that loads one large 768KB image from a remote server.
In our tests, we compare page load times using both plain HTTP and \zbf in a range of
scenarios. Specifically, we varied two parameters: the number of seeding peers and the
number of leeching peers. A seeding peer is a peer that has the desired resource, which
in our tests, was the single image on the site. A leeching peer is a peer that desires the
resource, so must request it either from the central site host or from peers with the resource.
Our tests launched a certain number of seeding peers, then launched a number of
leeching peers, measuring the average load latency for the leeching peers. We compare
this latency data with the page load latency when the leeching peers must load the content from the
central site host.

\subsection{Simulating the "reddit effect"}

Our tests involved programmatically opening browser windows and measuring load times.
Due to limitations of the number of browser windows that can be reasonably opened
and the memory overhead of Chrome, our browser testing environment of choice, we could
not reasonably open enough browser windows to exactly imitate millions of simultaneous
visitors to a site. Instead, we simulated the "reddit effect" by throttling the content delivery
bandwidth of the central server hosting the desired resource.

@@

% TODO selenium & scala
% anish should probably do this section

\subsection{Results}

@@

There remains numerous optimizations that would make \zbf more performant
when used on a deployed, high-traffic site. We detail these potential optimization
in this section.

@@

% TODO cite peercdn in bibtex
Currently, alternative peer-to-peer content delivery networks do exist. The three
prominent peer-to-peer CDNs are PeerJS, PeerCDN, and Peer5. PeerJS is open-sourced
and similarly transparent, but only encapsulates the functionality of our connection manager
module. PeerCDN~\cite{peercdn} is a closed-source alternative providing  similar
functionality to \zbf; it offloads site content delivery to users of a site,
significantly lowering strain on the central source. However, PeerCDN was acquired by
Yahoo! and no longer exists. Finally, Peer5 is a service used by companies today.
Unfortunately, Peer5 is a paid service that is entirely closed-source; the Peer5 code is
not transparent to the clients on which it runs.

@@

% Katie
\zbf is an open-sourced system
that will allow developers to easily integrate a peer-to-peer CDN to expedite
content delivery to clients even when operating under heavy load.

>>>>

\subsection{DOM injection layer}
The DOM injection layer facilitates the link between the DOM as displayed in the browser and the entire peer-to-peer system. The DOM injection layer creates a WebSocket, and then instantiates a Tracker and Signaling Channel. It uses these to then instantiate a Connection Manager and in turn, uses this to instantiate a Download Manager.

@@

\subsection{Server implementation}

@@

\subsubsection{Tracker}
The tracker is hosted on a remote server and tracks client connections.
The client-side tracker interface opens a WebSocket connection with the remote tracker,
which registers the existence of this client. The remote tracker responds to
requests from the client for lists of peers with a given resource. When a client
publicizes that it has a resource through the tracker interface, the remote tracker updates
the list of peers with the resource to include this client, as
long as its WebSocket connection remains open. Upon WebSocket disconnection,
the tracker ``forgets'' about the client and erases all data about the client's
held resources.

\subsubsection{WebRTC handshake channel}

@@

We tested \zbf on a simple site that loads one large 768KB image from a remote server.
In our tests, we compare page load times using both plain HTTP and \zbf in a range of
scenarios. Specifically, we varied two parameters: the number of seeding peers and the
number of leeching peers. A seeding peer is a peer that has the desired resource, which
in our tests, was the single image on the site. A leeching peer is a peer that desires the
resource, so must request it either from the central site host or from peers with the resource.

Our tests launched a certain number of seeding peers, then launched a number of
leeching peers, measuring the average load latency for the leeching peers. We compare
this latency data with the page load latency when the leeching peers must load the content from the
central site host.

\subsection{Simulating the "reddit effect"}
Our tests involved programmatically opening browser windows and measuring load times.
Due to limitations of the number of browser windows that can be reasonably opened
and the memory overhead of Chrome, our browser testing environment of choice, we could
not reasonably open enough browser windows to exactly imitate millions of simultaneous
visitors to a site. Instead, we simulated the "reddit effect" by throttling the content delivery
bandwidth of the central server hosting the desired resource. We limited the content delivery
rate to 64 Kb/s and performed benchmark tests that compared the performance of \zbf 
against the HTTP content delivery latency under the throttled bandwidth conditions.

@@

% TODO selenium with chromedriver & scala
% anish should probably do this section

\subsection{Results}
 % TODO

\subsubsection{Scalability of \zbf}
The first empirical analysis that we performed was determining how page load time over \zbf scales as we vary the number of users who have the page loaded (we call these users \textit{seeders}) and the number of users attempting to concurrently download the page (we call these users \textit{leechers}).

\begin{figure}[h]
% TODO: heatmap here
\caption{Average page load time over P2P for seeders vs leechers}
\end{figure}

\subsubsection{\zbf vs HTTP}
% TODO: figure out ratio of seeders to leechers
Our next empirical analysis was to keep the ratio of seeders to leechers constant at X, and compare the page load times for a throttled HTTP server vs \zbf as we increase the number of users attempting to concurrently load the page.

\begin{figure}[h]
% TODO: other plot here
% TODO: figure out ratio of seeders to leechers
\caption{Average page load time over P2P compared to HTTP on throttled server assuming constant ratio of X seeders per leecher}
\end{figure}

@@

There remains numerous optimizations that would make \zbf more performant
when used on a deployed, high-traffic site. We detail these potential optimizations
in this section, along with features which could allow \zbf to handle more use cases.

@@

%! TODO cite peercdn in bibtex
Currently, alternative peer-to-peer content delivery networks do exist. The three
prominent peer-to-peer CDNs are PeerJS, PeerCDN, and Peer5. PeerJS is open-sourced
and similarly transparent, but only encapsulates the functionality of our connection manager
module. PeerCDN~\cite{peercdn} is a closed-source alternative providing  similar
functionality to \zbf; it offloads site content delivery to users of a site,
significantly lowering strain on the central source. However, PeerCDN was acquired by
Yahoo! and no longer exists. Finally, Peer5 is a service used by companies today.
Unfortunately, Peer5 is a paid service that is entirely closed-source; the Peer5 code is
not transparent to the clients on which it runs.

@@

% TODO: Katie
\zbf is an open-sourced system
that will allow developers to easily integrate a peer-to-peer CDN to expedite
content delivery to clients even when operating under heavy load.
